Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-19 manuscript.Rmd
Forgot to save before push.

@@

>>>>

lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))

sm.df.reduced <- sm.df %>% select(-Overall.N)

@@

DataBase <- rep("Scopus", nrow(scopus.df))
scopus.df$DataBase <- DataBase
scopus.df$Documents <- ifelse(scopus.df$Documents == 0, NA, scopus.df$Documents)

DataBase <- rep("HD", nrow(sm.df.reduced))
sm.df.reduced$DataBase <- DataBase
sm.df.reduced <- sm.df.reduced %>% rename(Documents = N) 
sm.df.reduced$Documents <- ifelse(sm.df.reduced$Documents == 0, NA, sm.df.reduced$Documents)  
sm.df.reduced <- na.omit(sm.df.reduced)

combined <- rbind(scopus.df, sm.df.reduced)
combined_reduced <- combined[combined$Journal %in% c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work", "Journal of Social Work Education"), ]

ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line() + 
     facet_wrap(~ Journal)
